Predicting Covid Data

### 2022-12-01 jin_sim.Rmd

# find the second derivative of fitted function
# source: https://proofwiki.org/wiki/Derivative_of_Error_Function
  erf_deriv <- function(x) {2/sqrt(pi)*exp(-x^2)}
  fn_try_deriv <- bquote(.(est_try[2]) * 2/sqrt(pi) * exp(-(.(est_try[3]) * x - .(est_try[4]))^2))
  fn_try_deriv <- D(fn_try_deriv,'x')
  x=seq(1,67,length.out=6700)
  tmp <- eval(fn_try_deriv)
  flex_day[i] <- min(x[tmp < 0])
}
flex_day
```

>>>>

# find the second derivative of fitted function
# source: https://proofwiki.org/wiki/Derivative_of_Error_Function
  erf_deriv <- function(x) {2/sqrt(pi)*exp(-x^2)}
  fn_try_deriv <- bquote(.(est_try[2]) * 2/sqrt(pi) * exp(-(.(est_try[3]) * x - .(est_try[4]))^2))
  fn_try_deriv <- D(fn_try_deriv,'x')
  x=seq(1,67,length.out=6700)
  tmp <- eval(fn_try_deriv)
  flex_day[i] <- min(x[tmp < 0])
}

mean(flex_day)
sd(flex_day)
```

## MC (day of flex) plot

```{r}
ggplot() +
  geom_point(aes(x=1:m, y=flex_day), color="red") +
  geom_hline(yintercept=mean(flex_day), color="blue") +
  labs(x = "Number of Monte Carlo simulation", y = "Day of flex, from February 15")
```

### 2022-12-01 main.rmd
Changes to main.rmd

@@

## (Fill in Here) Simulation

## Works Cited

- Add link to study here
- Add link to covid data here

>>>>

# China Simulation

## China Simulation

# Italy Simulation

@@

## Works Cited
- Link to study:
- I. Ciufolini, A. Paolozzi, Prediction of the time evolution of the Covid-19 Pandemic in Italy by a Gauss
Error Function and Monte Carlo simulations. Submitted to BioRxiv on 03.26.2020 and transferred on
03.27.2020 to MedRxiv. https://doi.org/10.1101/2020.03.27.20045104
- Link to covid data:
- https://covid19.who.int/
